supplements_webcamcoding

### 2022-04-29 stats/supplements_webcamcoding.Rmd
edit extvali and webcam coding posterior draws

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(brms)
library(ggridges)

@@

```{r webcam_perTrial_models}
# originally: 
# brm(correct ~ age + (trial + targetPosition | subjID) + (age | targetPosition)
# age + person effect + trial effect
# simplified the model, since not a lot of data / info to estimate all the parameters. 
# therefore, remove trial & targetposition

@@

mPerTrialComparison <- as_tibble(mPerTrialComparison, rownames = "model")
write.csv(mPerTrialComparison, "../saves/supplements-webcamcoding-mPerTrialComparison-WAIC.csv", quote = F, row.names = F)
saveRDS(mPerTrialComparison, "../saves/supplements-webcamcoding-mPerTrialComparison-WAIC.rds")

mPerTrialComparisonWeights <- as_tibble(model_weights(mPerTrialNull, mPerTrialPI, mPerTrialRepeatedTestquestion, mPerTrialVerificationChoice, mPerTrialHintsEyes, mPerTrialParentSpeech, criterion = "waic"), rownames = "model")
write.csv(mPerTrialComparisonWeights, "../saves/supplements-webcamcoding-mPerTrialComparison-weights.csv", quote = F, row.names = F)
saveRDS(mPerTrialComparisonWeights, "../saves/supplements-webcamcoding-mPerTrialComparison-weights.rds")
```

```{r webcam_perTrial_plot}
postSamplesPerTrial <- bind_rows(
  # posterior_samples(mPerTrialNull, pars = "age") %>% mutate(model = "mPerTrialNull - age") %>% rename(estimate = b_age),
  posterior_samples(mPerTrialPI, pars = "pi") %>% mutate(model = "mPerTrialPI") %>% rename(estimate = b_pi), 
  posterior_samples(mPerTrialRepeatedTestquestion, pars = "repeatedTestquestion") %>% mutate(model = "mPerTrialRepeatedTestquestion") %>% rename(estimate = b_repeatedTestquestion), 
  posterior_samples(mPerTrialVerificationChoice, pars = "verificationChoice") %>% mutate(model = "mPerTrialVerificationChoice") %>% rename(estimate = b_verificationChoice), 
  posterior_samples(mPerTrialHintsEyes, pars = "hintsEyes") %>% mutate(model = "mPerTrialHintsEyes") %>% rename(estimate = b_hintsEyes), 
  posterior_samples(mPerTrialParentSpeech, pars = "parentSpeech") %>% mutate(model = "mPerTrialParentSpeech") %>% rename(estimate = b_parentSpeech), 
)

postSamplesPerTrial <- postSamplesPerTrial %>% 
  mutate(
        model = factor(model, levels = c("mPerTrialParentSpeech", "mPerTrialHintsEyes", "mPerTrialVerificationChoice", "mPerTrialRepeatedTestquestion", "mPerTrialPI")),
  )

ggplot(postSamplesPerTrial, aes(x = estimate, y = model, fill = factor(stat(quantile)))) +
  geom_vline(xintercept = 0, lty = 2, alpha = .75) +
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE, 
    quantiles = c(0.025, 0.975)
  ) +	
  scale_fill_manual(values = c("firebrick", "NA", "firebrick"), guide = "none") +
  scale_x_continuous(limits = c(-2, 2), breaks = seq(-2, 2, by = 0.5))

ggsave("../figures/supplements-webcamcoding-mPerTrialComparison-posteriorsample.png")
```

@@

```{r webcam_perTrial_comparisons}
mPerSubjectNull <- add_criterion(mPerSubjectNull, "waic")
mPerSubjectPI <- add_criterion(mPerSubjectPI, "waic")
mPerSubjectRepeatedTestquestion <- add_criterion(mPerSubjectRepeatedTestquestion, "waic")
mPerSubjectVerificationChoice <- add_criterion(mPerSubjectVerificationChoice, "waic")
mPerSubjectHintsEyes <- add_criterion(mPerSubjectHintsEyes, "waic")
mPerSubjectParentSpeech <- add_criterion(mPerSubjectParentSpeech, "waic")

@@

mPerSubjectComparison <- as_tibble(mPerSubjectComparison, rownames = "model")
write.csv(mPerSubjectComparison, "../saves/supplements-webcamcoding-mPerSubjectComparison-WAIC.csv", quote = F, row.names = F)
saveRDS(mPerSubjectComparison, "../saves/supplements-webcamcoding-mPerSubjectComparison-WAIC.rds")

mPerSubjectComparisonWeights <- as_tibble(model_weights(mPerSubjectNull, mPerSubjectPI, mPerSubjectRepeatedTestquestion, mPerSubjectVerificationChoice, mPerSubjectHintsEyes, mPerSubjectParentSpeech, criterion = "waic"), rownames = "model")
write.csv(mPerSubjectComparisonWeights, "../saves/supplements-webcamcoding-mPerSubjectComparison-weights.csv", quote = F, row.names = F)
saveRDS(mPerSubjectComparisonWeights, "../saves/supplements-webcamcoding-mPerSubjectComparison-weights.rds")
```

```{r webcam_perTrial_plot}
postSamplesPerSubject <- bind_rows(
  # posterior_samples(mPerTrialNull, pars = "age") %>% mutate(model = "mPerTrialNull - age") %>% rename(estimate = b_age),
  posterior_samples(mPerSubjectPI, pars = "pi") %>% mutate(model = "mPerSubjectPI") %>% rename(estimate = b_pi), 
  posterior_samples(mPerSubjectRepeatedTestquestion, pars = "repeatedTestquestion") %>% mutate(model = "mPerSubjectRepeatedTestquestion") %>% rename(estimate = b_repeatedTestquestion), 
  posterior_samples(mPerSubjectVerificationChoice, pars = "verificationChoice") %>% mutate(model = "mPerSubjectVerificationChoice") %>% rename(estimate = b_verificationChoice), 
  posterior_samples(mPerSubjectHintsEyes, pars = "hintsEyes") %>% mutate(model = "mPerSubjectHintsEyes") %>% rename(estimate = b_hintsEyes), 
  posterior_samples(mPerSubjectParentSpeech, pars = "parentSpeech") %>% mutate(model = "mPerSubjectParentSpeech") %>% rename(estimate = b_parentSpeech), 
)

postSamplesPerSubject <- postSamplesPerSubject %>% 
  mutate(
        model = factor(model, levels = c("mPerSubjectParentSpeech", "mPerSubjectHintsEyes", "mPerSubjectVerificationChoice", "mPerSubjectRepeatedTestquestion", "mPerSubjectPI")),
  )

ggplot(postSamplesPerSubject, aes(x = estimate, y = model, fill = factor(stat(quantile)))) +
  geom_vline(xintercept = 0, lty = 2, alpha = .75) +
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE, 
    quantiles = c(0.025, 0.975)
  ) +	
  scale_fill_manual(values = c("firebrick", "NA", "firebrick"), guide = "none")

ggsave("../figures/supplements-webcamcoding-mPerSubjectComparison-posteriorsample.png")
```

```{r overall_save}
overall_results <- bind_rows(mPerTrialComparison, mPerSubjectComparison) %>% 
  left_join(bind_rows(mPerTrialComparisonWeights, mPerSubjectComparisonWeights)) %>% 
  select(model, waic, value, elpd_diff, se_diff) %>% 
  rename(waic_weight = value)

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(brms)
library(ggridges)
library(ggpubr)
library(tidybayes)

@@

```{r webcam_perTrial_models}
# originally: 
# brm(correct ~ age + (symmetricPosition | subjID) + (1 | targetPosition)
# age + person effect + trial effect
# simplified the model, since not a lot of data / info to estimate all the parameters. 
# therefore, remove trial & targetposition

@@

mPerTrialComparison <- as_tibble(mPerTrialComparison, rownames = "model")

mPerTrialComparisonWeights <- as_tibble(model_weights(mPerTrialNull, mPerTrialPI, mPerTrialRepeatedTestquestion, mPerTrialVerificationChoice, mPerTrialHintsEyes, mPerTrialParentSpeech, criterion = "waic"), rownames = "model")
```

```{r webcam_perTrial_posteriordraws}
perTrial_draws <- bind_rows(
  mPerTrialPI %>% gather_draws(b_pi),
  mPerTrialRepeatedTestquestion %>% gather_draws(b_repeatedTestquestion), 
  mPerTrialVerificationChoice %>% gather_draws(b_verificationChoice), 
  mPerTrialHintsEyes %>% gather_draws(b_hintsEyes), 
  mPerTrialParentSpeech %>% gather_draws(b_parentSpeech), 
  ) %>% 
  mutate(
    Predictor = factor(.variable, 
                       levels = c("b_verificationChoice", 
                                  "b_pi", 
                                  "b_repeatedTestquestion", 
                                  "b_parentSpeech", 
                                  "b_hintsEyes"
                       ), 
                       labels = c("# Verification choice", 
                                  "Parental interference index",
                                  "# Repeated testquestion", 
                                  "# Words uttered by caregiver", 
                                  "# Hints towards eyes"
                       )
                )  
  )

write.csv(perTrial_draws, "../saves/supplements-webcamcoding-perTrialdraws.csv", quote = F, row.names = F)
saveRDS(perTrial_draws, "../saves/supplements-webcamcoding-perTrialdraws.rds")
```

```{r webcam_perTrial_plot}
perTrial_plot <- perTrial_draws %>% 
  ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
 tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80)) +
    labs(x = "Posterior estimate", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("grey","#85AD00")) +
  scale_x_continuous(limits = c(-2, 2), breaks = seq(-2, 2, 0.5)) +
  theme_minimal()

perTrial_plot

ggsave("../figures/supplements_webcamcoding_perTrial.png", width = 10, height = 6, scale = 0.7, bg = "white")
```

@@

```{r webcam_perSubject_comparisons}
mPerSubjectNull <- add_criterion(mPerSubjectNull, "waic")
mPerSubjectPI <- add_criterion(mPerSubjectPI, "waic")
mPerSubjectRepeatedTestquestion <- add_criterion(mPerSubjectRepeatedTestquestion, "waic")
mPerSubjectVerificationChoice <- add_criterion(mPerSubjectVerificationChoice, "waic")
mPerSubjectHintsEyes <- add_criterion(mPerSubjectHintsEyes, "waic")
mPerSubjectParentSpeech <- add_criterion(mPerSubjectParentSpeech, "waic")

@@

mPerSubjectComparison <- as_tibble(mPerSubjectComparison, rownames = "model")

mPerSubjectComparisonWeights <- as_tibble(model_weights(mPerSubjectNull, mPerSubjectPI, mPerSubjectRepeatedTestquestion, mPerSubjectVerificationChoice, mPerSubjectHintsEyes, mPerSubjectParentSpeech, criterion = "waic"), rownames = "model")
```

```{r webcam_perSubject_posteriordraws}
perSubject_draws <- bind_rows(
  mPerSubjectPI %>% gather_draws(b_pi),
  mPerSubjectRepeatedTestquestion %>% gather_draws(b_repeatedTestquestion), 
  mPerSubjectVerificationChoice %>% gather_draws(b_verificationChoice), 
  mPerSubjectHintsEyes %>% gather_draws(b_hintsEyes), 
  mPerSubjectParentSpeech %>% gather_draws(b_parentSpeech), 
  ) %>% 
  mutate(
    Predictor = factor(.variable, 
                       levels = c("b_verificationChoice", 
                                  "b_pi", 
                                  "b_repeatedTestquestion", 
                                  "b_parentSpeech", 
                                  "b_hintsEyes"
                       ), 
                       labels = c("# Verification choice", 
                                  "Parental interference index",
                                  "# Repeated testquestion", 
                                  "# Words uttered by caregiver", 
                                  "# Hints towards eyes"
                       )
                )
  )

write.csv(perSubject_draws, "../saves/supplements-webcamcoding-perSubjectdraws.csv", quote = F, row.names = F)
saveRDS(perSubject_draws, "../saves/supplements-webcamcoding-perSubjectdraws.rds")
```

```{r webcam_perSubject_plot}
perSubject_plot <- perSubject_draws %>% 
  ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
 tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80), scale = 1.75) +
    labs(x = "Posterior estimate", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("grey","#85AD00")) +
  scale_x_continuous(limits = c(-1, 0.75), breaks = seq(-1, 0.75, 0.25)) +
  theme_minimal()

perSubject_plot

ggsave("../figures/supplements_webcamcoding_perSubject_draws.png", width = 10, height = 6, scale = 0.7, bg = "white")
```

```{r combined_plot}
ggarrange(perTrial_draws %>% 
            ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
            tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80)) +
            labs(x = "Posterior estimate", y = "") +
            guides(fill = "none")+
            geom_vline(xintercept = 0, linetype = "dashed") +
            scale_fill_manual(values = c("grey","#85AD00")) +
            scale_x_continuous(limits = c(-2, 2), breaks = seq(-2, 2, 1)) +
            theme_minimal() + 
            theme(panel.grid.minor.x = element_blank()),

          ggarrange(
            perSubject_draws %>% 
              ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
              tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80), scale = 2) +
              labs(x = "", y = "") +
              guides(y = "none", fill = "none") +
              geom_vline(xintercept = 0, linetype = "dashed") +
              scale_fill_manual(values = c("grey","#85AD00")) +
              scale_x_continuous(limits = c(-1, 0.75), breaks = seq(-1, 0.75, 0.5)) +
              theme_minimal(), 
            NULL, 
            nrow = 2, heights = c(1, 0.0001)
          ),

          nrow = 1, widths = c(1, 0.75),
          labels = c("A", "B")
          )

ggsave("../figures/supplements_webcamcoding_draws.png", width = 10, height = 6, scale = 0.7, bg = "white")
```

```{r overall_save}
overall_results <- bind_rows(mPerTrialComparison, mPerSubjectComparison) %>% 
  left_join(bind_rows(mPerTrialComparisonWeights, mPerSubjectComparisonWeights)) %>% 
  select(model, waic, value, elpd_diff, se_diff) %>% 
  rename(
    Predictor = model, 
    WAIC = waic, 
    Weight = value, 
    ELPD = elpd_diff, 
    SE = se_diff,
  ) %>% 
  mutate(
    Predictor = recode(Predictor, 
                   "mPerTrialVerificationChoice" = "By trial - # Verification choice", 
                   "mPerTrialNull" = "By trial - Null model", 
                   "mPerTrialPI" = "By trial - Parental interference index", 
                   "mPerTrialRepeatedTestquestion" = "By trial - # Repeated testquestion", 
                   "mPerTrialParentSpeech" = "By trial - # Words uttered by caregiver", 
                   "mPerTrialHintsEyes" = "By trial - # Hints eyes", 
                   "mPerSubjectRepeatedTestquestion" = "By subject - # Repeated testquestion", 
                   "mPerSubjectPI" = "By subject - Parental interference index", 
                   "mPerSubjectNull" = "By subject - Null model", 
                   "mPerSubjectVerificationChoice" = "By subject - # Verification choice", 
                   "mPerSubjectParentSpeech" = "By subject - # Words uttered by caregiver", 
                   "mPerSubjectHintsEyes" = "By subject - # Hints eyes"
                   )
  )

overall_results
